explore networkx

### 2019-12-17 scripts/explore-networkx.Rmd
separate graphs by lc

```{python}
import pandas as pd
import networkx as nx

edges = pd.read_csv('../data/edgels.csv')
edges
G=nx.from_pandas_edgelist(edges, 'V1', 'V2', edge_attr='w')
```

>>>>

```{python}
import pandas as pd
import networkx as nx
import multinetx as ml

edges = pd.read_csv('../data/edgels.csv')

print(edges['relc'].unique())

G1 = nx.from_pandas_edgelist(edges[edges['relc'] == 1], 'V1', 'V2', edge_attr='w')
G2 = nx.from_pandas_edgelist(edges[edges['relc'] == 2], 'V1', 'V2', edge_attr='w')
G3 = nx.from_pandas_edgelist(edges[edges['relc'] == 3], 'V1', 'V2', edge_attr='w')

```
